### 2020-04-16 Report/aws_325ghz_study.tex
Another script for figures of wfund and transmissivities.

\noindent
\textbf{\Large Study to support the definition of Arctic Weather \vspace{1mm}\\
Satellite (AWS) high frequency channels} \vspace{8mm}\\
{\bf Patrick Eriksson, Simon Pfreundschuh and Inderpreet Kaur}\\
Department of Space, Earth and Environment\\
Chalmers University of Technology\\
SE-412\,96, Gothenburg, Sweden \vspace{10mm}

@@

\begin{table}[!bt]
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-21  & \phantom{0}89.000 & 4000\\
    AWS-31  & 165.500 & 2800\\
    AWS-32  & 176.311 & 2000\\
    AWS-33  & 178.811 & 2000\\
    AWS-34  & 180.311 & 1000\\
    AWS-35  & 181.511 & 1000\\
    AWS-36  & 182.311 & \phantom{0}500\\
    AWS-41  & 229.000 & 2000\\
    \hline
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    ICI-5  & 325.15$\pm$9.50 & 3000\\
    ICI-6  & 325.15$\pm$3.50 & 2400\\
    ICI-7  & 325.15$\pm$1.50 & 1600\\
    \hline
  \end{tabular}
  \end{minipage}  
  \caption{Fixed channel position and widths. The left table covers channels of
    AWS, with values taken from SoW. Channels AWS-21 to AWS-36 are at this
    moment mandatory for AWS, while AWS-41 is so far tentative. The right table
    lists the values of some channels of ICI \citep{eriksson:towar:20}.}
  \label{tab:fixed:chs}
\end{table}

@@

\section{Results}

\subsection{Overview of the 183, 229 and 325\,GHz bands}
%
The simulations in this section are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$. No hydrometeors are included. For simpler interpretation of the
results, the reflectivity is set to have no frequency variation, i.e.\ the same
value is applied for all bands. The reflective is varied between 0 and 0.5.
In the figures covering transmissivities and Jacobians, the specifications
of ICI is applied for 325\,GHz channels (Table~\ref{tab:fixed:chs}).

\subsubsection{Clear-sky brightness temperatures}
%
Figure~\ref{fig:tb:r000} shows brightness temperatures over the three bands, for
a reflectivity of 0 (i.e.\ a blackbody surface). The figure takes into account
that the 183\,GHz channels of AWS are of single-sideband character, while for
229 and 325\,GHz averages of upper and lower sidebands are shown, plotted as
a function from the centre frequency on the lower side.

@@

\subsubsection{Clear-sky transmissivities to space}
%
Assuming that a cloud layer can be moved in altitude, its impact on measured
brightness temperatures will roughly follow the transmissivity to space for the
cloud altitude. In short, where the transmissivity is zero the cloud will have
no impact, while where the transmissivity is unity the influence will be close
to constant with altitude (especially when the single scattering albedo is
high). This relationship just refers to the relative impact for a
given frequency, the absolute impact (at transmissivity 1) increases in general
with frequency.

@@

\subsubsection{Clear-sky relative humidity weighting functions}
%
The sensitivity to humidity is most easily compared by the channels' weighting
functions (i.e.\ the Jacobian), and examples are found in
Fig.~\ref{fig:wf:mls:025}. The shape of the weighting functions depends on the
unity selected for representing water vapour. As the absolute amount of water
vapour varies with orders of magnitude from the surface to the tropopause, it
is difficult to interpret weighting functions for absolute humidity units and
it is more suitable to use a relative one. In Fig.~\ref{fig:wf:mls:025} the
weighting functions correspond to an increase of relative humidity (RH) with one
percent unit over 1\,km. RH with respect liquid/ice is applied above/below
0$^\circ$C.

@@

@@

\bibliography{j_abbr,references}

>>>>

\thispagestyle{empty}
\noindent
\textbf{\Large Study to support the definition of Arctic Weather \vspace{1mm}\\
Satellite (AWS) high frequency channels} \vspace{8mm}\\
{\bf Patrick Eriksson, Simon Pfreundschuh and Inderpreet Kaur}\\
Department of Space, Earth and Environment\\
Chalmers University of Technology\\
SE-412\,96, Gothenburg, Sweden \vspace{10mm}

\section*{Summary}
%
To written \dots

\setcounter{tocdepth}{1} 
\tableofcontents

\newpage
\setcounter{page}{1}

@@

\begin{table}[!b]
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-21  & \phantom{0}89.000 & 4000\\
    AWS-31  & 165.500 & 2800\\
    AWS-32  & 176.311 & 2000\\
    AWS-33  & 178.811 & 2000\\
    AWS-34  & 180.311 & 1000\\
    AWS-35  & 181.511 & 1000\\
    AWS-36  & 182.311 & \phantom{0}500\\
    AWS-41  & 229.000 & 2000\\
    \hline
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    ICI-5  & 325.15$\pm$9.50 & 3000\\
    ICI-6  & 325.15$\pm$3.50 & 2400\\
    ICI-7  & 325.15$\pm$1.50 & 1600\\
    \hline
  \end{tabular}
  \end{minipage}  
  \caption{Fixed channel position and widths. The left table covers channels of
    AWS, with values taken from SoW. Channels AWS-21 to AWS-36 are at this
    moment mandatory for AWS, while AWS-41 is so far tentative. The right table
    lists the values of some channels of ICI \citep{eriksson:towar:20}.}
  \label{tab:fixed:chs}
\end{table}

@@

\section{Overview of the 183, 229 and 325\,GHz bands}
%
The simulations in this section are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$. No hydrometeors are included. For simpler interpretation of the
results, the reflectivity is set to have no frequency variation, i.e.\ the same
value is applied for all bands. The reflective is varied between 0 and 0.5.
In the figures covering transmissivities and Jacobians, the specifications
of ICI is applied for 325\,GHz channels (Table~\ref{tab:fixed:chs}).

\subsection{Clear-sky brightness temperatures}
%
Figure~\ref{fig:tb:r000} shows brightness temperatures over the three bands, for
a reflectivity of 0 (i.e.\ a blackbody surface). The figure takes into account
that the 183\,GHz channels of AWS are of single-sideband character, while for
229 and 325\,GHz averages of upper and lower sidebands are shown, plotted as
a function from the centre frequency on the lower side.

@@

\subsection{Clear-sky transmissivities to space}
%
Assuming that a cloud layer can be moved in altitude, its impact on measured
brightness temperatures will roughly follow the transmissivity to space for the
cloud altitude. In short, where the transmissivity is zero the cloud will have
no impact, while where the transmissivity is unity the influence will be close
to constant with altitude (especially when the single scattering albedo is
high). This relationship just refers to the relative impact for a
given frequency, the absolute impact (at transmissivity 1) increases in general
with frequency.

@@

\subsection{Clear-sky relative humidity weighting functions}
%
The sensitivity to humidity is most easily compared by the channels' weighting
functions (i.e.\ the Jacobian), and examples are found in
Fig.~\ref{fig:wf:mls:025}. The shape of the weighting functions depends on the
unity selected for representing water vapour. As the absolute amount of water
vapour varies with orders of magnitude from the surface to the tropopause, it
is difficult to interpret weighting functions for absolute humidity units and
it is more suitable to use a relative one. In Fig.~\ref{fig:wf:mls:025} the
weighting functions correspond to an increase of relative humidity (RH) with one
percent unit over 1\,km. RH with respect liquid/ice is applied above/below
0$^\circ$C.

@@

\section{Preliminary options for 325\,GHz channels}

\subsection{...}
%
\dots Fig.~\ref{fig:wfuns:325ul}

\begin{figure}[!tb]
  \centering
  \includegraphics[height=65mm]{fascod_wf_325l_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=65mm]{fascod_wf_325u_tro}
 \caption{...}
  \label{fig:wfuns:325ul}
\end{figure}

@@

{\footnotesize
\bibliography{j_abbr,references}
}
